insert title here

### 2020-12-10 Simulations.Rmd
Update Simulations.Rmd
fix THE BUG

# The Model
```{r}
set.seed(40)
# There are three key parameters: the probability that the worst team in the league beats the best team in a random game (given by 'p'), the standard deviation in game-to-game performance levels for each team (given by 'tao'), and the standard deviation in the team talent levels (given by 'sigma'). We as the researchers choose a value for p or the ratio of tao and sigma.
p = 0.25
tao = 4.28
sigma = 1

@@

c(mean(oldGap), mean(newGap))
```

@@

returnOldWestern <- function(points) {
  central = points[points$id %in% c(16:19, 29),]
  northwest = points[points$id %in% c(20:23, 30),]
  pacific = points[points$id %in% c(26:28),]

>>>>

# The Model
```{r}
set.seed(405)
# There are three key parameters: the probability that the worst team in the league beats the best team in a random game (given by 'p'), the standard deviation in game-to-game performance levels for each team (given by 'tao'), and the standard deviation in the team talent levels (given by 'sigma'). We as the researchers choose a value for p or the ratio of tao and sigma.
p = 0.25
tao = 4.28
sigma = 1

@@

c(mean(oldGap), mean(newGap), mean(newGap - oldGap))
```

@@

returnOldWestern <- function(points) {
  central = points[points$id %in% c(16:19, 29),]
  northwest = points[points$id %in% c(20:23, 30),]
  pacific = points[points$id %in% c(24:28),]

### 2020-12-10 slides.Rmd
remove useless files (new format)
fix THE BUG

>>>>

# The Model: Goals

- To simulate the performance of each team over a season with varying rules
- To create an accurate scoring system that accounts for ties

# The Model: Goals

- To simulate the performance of each team over a season with varying rules
- To create an accurate scoring system that accounts for ties
- (For me) to learn how hockey works!

# The Model: Methods

- We generate each team's "quality" from a normal distribution
- For each of the games played we generate a "game performance" metric from a normal distribution with the mean being the respective team's quality.

![Quality Metric](Images/teamQuality.png)
![Game Performance](Images/teamPerformance.png)

# The Model: Methods

- A game will go into overtime ~ 22.4% of the time
- If the teams skills are within a threshold alpha, it will go into overtime
- Once in overtime rescale performances and determine winner by weighted coinflip

# The Model: Methods

- We simulate 10,000 seasons to gather our metrics
- Sort teams into the right conference, then into the right division based on which set of rules we are looking at (old or new)
- Calculate the conference gap

# 2013-2014 Season Results

- We have found
